### 2020-11-17 ReadMe.rmd
update readme for final release

| [GitHub page (latest)](https://vlucet.github.io/landchange-connectivity-monteregie/) | [Thesis PDF (latest)](https://github.com/VLucet/landchange-connectivity-monteregie/blob/master/thesis/build/thesis.pdf) | [Initial Submission Release](https://github.com/VLucet/landchange-connectivity-monteregie/releases/tag/v1.0)
|:-------------:|:-------------:|:-----:|

>>>>

| [GitHub page (latest)](https://vlucet.github.io/landchange-connectivity-monteregie/) | [Thesis PDF (latest)](https://github.com/VLucet/landchange-connectivity-monteregie/blob/master/thesis/build/thesis.pdf) | [Initial Submission Release](https://github.com/VLucet/landchange-connectivity-monteregie/releases/tag/v1.0) | [Final Submission Release](https://github.com/VLucet/landchange-connectivity-monteregie/releases/tag/v2.0)
|:-----:|:-----:|:-----:|:-----:|
